---
title: "Homework 3_4"
author: "JP"
date: "11/12/2020"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Loading Data

```{r load in data}
library(tidyverse)
library(lavaan)
library(lavaanPlot)

hw <- rio::import(here::here('data', 'hw4_achievement.csv'),
                  setclass = 'tbl_df') %>% 
  janitor::clean_names()
```

```{r modeling}
psych::describe(hw, na.rm = TRUE)

hw2 <- hw %>% 
  mutate(efficacy_z = scale(efficacy, center = TRUE, scale = TRUE),
         bullying_z = scale(bullying, center = TRUE, scale = TRUE),
         eff_x_bull = efficacy_z*bullying_z,
         bully_minus = bullying_z - 1,
         bully_plus = bullying_z + 1)

model <- lm(achieve_t ~ efficacy_z*bullying_z + girl, data = hw2)
summary(model)

minus <- lm(achieve_t ~ efficacy_z*bully_minus + girl, data = hw2)
summary(minus)

plus <- lm(achieve_t ~ efficacy_z*bully_plus + girl, data = hw2)
summary(plus)

lav_mod <- '
# regression
achieve_t ~ efficacy_z + bullying_z + eff_x_bull + girl
'

lav_fit <- sem(lav_mod, data = hw2)
summary(lav_fit, standardized = TRUE)


hw2 %>%
  ggplot(aes(efficacy_z, achieve_t)) +
  geom_point(color = 'dodgerblue') +
  geom_abline(aes(linetype = '+ 1 SD',
                  slope = minus$coefficients['efficacy_z'],
                  intercept = minus$coefficients['(Intercept)']),
              size = 1) +
  geom_abline(aes(linetype = 'Average',
                  slope = model$coefficients['efficacy_z'],
                  intercept = model$coefficients['(Intercept)']),
              size = 1) +
  geom_abline(aes(linetype = '- 1 SD',
                  slope = plus$coefficients['efficacy_z'],
                  intercept = plus$coefficients['(Intercept)']),
              size = 1) +
  xlim(-2, 2)

```

## Plotting Interaction

```{r plotting}
library(probemod)

interactions::probe_interaction(model = model, pred = efficacy_z, modx = bullying_z)


jnresults <- jn(model, dv = 'achieve_t', iv = 'efficacy_z', mod = 'bullying_z', alpha = .05)

jnresults
plot(jnresults)

```

## Answers

My hypothesis is:

Higher levels of school bullying will moderate the impact of self-efficacy on achievement. Such that, higher levels of bullying will erode the beneficial effect of efficacy on achievement. 

Answer: 

The hypothesis was supported as bullying moderated the association between efficacy and achievement (b = -1.87, p < .001). The simple slopes showed that at all levels of bullying, the association between efficacy and achievement was significant. At high levels of bullying (-1 SD), self-efficacy was significantly associated with achievement (b = 5.02, p < .01). At low levels of bullying (+1 SD), self-efficacy was significantly associated with achievement (p < .001). The association was strongest for those that had lower levels of bullying. The regions of significance was within a lower bound of (6.66e-16, 2.02) and an upper bound of (-3.97, 2.20e-16). 

